SDR enhancement by clouds

### 2024-03-06 article/article.Rmd
Commit 2024-03-05 20:14
Commit 2024-03-06 11:10

@@

### Climatology

@@

>>>>

## Clear Sky Irradiance

In order to set a threshold for the CE we had to create a "clear sky" radiation approximation.
For that reason we decided to use the Libradtran model with climatological data from AERONET, Sun's total solar irradiance from NOAA and Earth - Sun distance calculated by Astropy.
We simulated radiation on multiple SZA's, for AOD at 500nm +/- 1 and 2 sigma, for watter column +/1 1 and 2 sigma, and for

@@

@@

```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
knitr::include_graphics("../images/energy-2.png")
```
